\documentclass[11pt,a4paper,landscape]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{fancyhdr}
\usepackage{multicol}

\author{Himanshu Mittal}
\title{Maxima And Minima}

\renewcommand{\labelenumi}{\theenumi}

\everymath{\displaystyle}
\pagestyle{fancy}
\fancyhf{}


\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{2pt}
\lfoot{\bfseries Himanshu Mittal : mittal01091997@gmail.com} 

\begin{document}
\begin{multicols*}{2}
{\noindent \bfseries {\Huge Maxima and Minima}}\\
\section{In Open Interval}
Let $y=f(x)$. The algorithm of finding maxima or minima is:
\renewcommand{\theenumi}{\Roman{enumi}}%
\begin{enumerate}
\item Find $\displaystyle{\frac{dy}{dx} = f'(x)}$
\item Put $f'(x)=0$ and solve for $x=c_1,\,c_2,\,c_3\,\cdots\,c_n$. These are possible points for maxima or minima.
\item Find $f''(x)$ or second derivative. Consider $x=c_1$.
	\begin{itemize}
	\item If $f''(x) < 0\Rightarrow$  Maxima
	\item If $f''(x) > 0\Rightarrow$  Minima
	\item If $f''(x) = 0\Rightarrow$  Find $f'''(x)$ or third derivative.
	\end{itemize}
\item If $f'''(x) \neq 0$, neither maxima nor minima. Check for $x=c_2,\,c_3\,\cdots\,c_n$
\item If $f'''(x) = 0$, find $f^{iv}$ or fourth derivative.
\item Consider $x=c_2$.
	\begin{itemize}
	\item If $f^{iv}(x) < 0\Rightarrow$  Maxima
	\item If $f^{iv}(x) > 0\Rightarrow$  Minima
	\item If $f^{iv}(x) = 0\Rightarrow$  Find $f^{v}(x)$ or fifth derivative.
	\end{itemize}
\item This process goes on.
\end{enumerate}

\vfill\null
\columnbreak

\section{In Closed Interval (Local Maxima and Minima)}

Let $y=f(x)$ defined on $[a, b]$. The Algorithm of finding Local Maxima or Minima is:
\renewcommand{\theenumi}{\Roman{enumi}}%
\begin{enumerate}
\item Find $\displaystyle{\frac{dy}{dx} = f'(x)}$
\item Put $f'(x)=0$ and solve for $x=c_1,\,c_2,\,c_3\,\cdots\,c_n$
\item Put Values in $f(x)$ and obtain values $f(a),\,f(c_1),\,f(c_2),\,\cdots\,f(c_n),\,f(b)$
\item The maximum and minimum values in the above list are Local maxima and minima for the function $y=f(x)$ in the range $[a,b]$ and the corresponding value $a\,\cdots\,c_n\,\cdots\,b$ is the point of local maxima or local minima.
\end{enumerate}
\end{multicols*}
\end{document}
